Experience Report: Haskell in Computational Biology

### 2012-07-01 everygen.tex
mk for noah

everyPt :: SearchGen pt r -> Age -> Scored pt
         -> Rand r [Aged (Utility (Scored pt))]
everyPt ss age startPt = do
  successors <- mapM (nextPt ss) (repeat startPt)
  tagged <- zipWithM agedUtility successors [succ age..]
  let (useless, Aged (Useful newPt) newAge : _) =
                        span (isUseless . unAged) tagged
  nextPts <- everyPt ss newAge newPt
  return $ Aged (Useful startPt) age : useless ++ nextPts

  where agedUtility pt age =
           utility ss move >>= \u -> return $ Aged u age
         where move = Move { older = startPt, younger = pt
                           , youngerAge = age }

>>>>

everyPt :: RandomGen r
        => SearchGen pt r -> CCost -> Scored pt
        -> Rand r [CCosted (Utility (Scored pt))]
everyPt sg cost startPt = do
  successors <- mapM (nextPt sg) (repeat startPt)
  tagged <- zipWithM costedUtility successors [succ cost..]
  let (useless, CCosted (Useful newPt) newCost : _) =
                      span (isUseless . unCCosted) tagged
  ((CCosted (Useful startPt) cost : useless) ++) <$>
                                  everyPt sg newCost newPt
 where costedUtility pt cost =
         utility sg move >>= \u -> return $ CCosted u cost
        where move = Move { older = startPt, younger = pt
                          , youngerCCost = cost }
